---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "images/README-",
  fig.width = 4,
  fig.height = 3
)
```

# transport

[![Travis-CI Build Status](https://travis-ci.org/ck37/transport.svg?branch=master)](https://travis-ci.org/ck37/transport)
[![AppVeyor Build  Status](https://ci.appveyor.com/api/projects/status/github/ck37/transport?branch=master&svg=true)](https://ci.appveyor.com/project/ck37/transport)
[![Coverage Status](https://img.shields.io/codecov/c/github/ck37/transport/master.svg)](https://codecov.io/github/ck37/transport?branch=master)

> Transportation estimators

## Description

TBD

## Installation

Install the development version from github:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ck37/transport")
```

## Examples

To be added.

## References

Rudolph, K. E., & Laan, M. J. (2017). [Robust estimation of encouragement design intervention effects transported across sites.](http://onlinelibrary.wiley.com/doi/10.1111/rssb.12213/full) Journal of the Royal Statistical Society: Series B (Statistical Methodology), 79(5), 1509-1525.

Rudolph, K. E., Schmidt, N. M., Glymour, M. M., Crowder, R., Galin, J., Ahern, J., & Osypuk, T. L. (2017). [Composition or context: using transportability to understand drivers of site differences in a large-scale housing experiment.](http://europepmc.org/abstract/med/29076878) Epidemiology (Cambridge, Mass.).
